### 2017-04-11 BOS/BOS.tex
Error Magnitudes Table

\documentclass{article}
\usepackage{geometry}
\usepackage{standalone}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{siunitx}
\usetikzlibrary{patterns,snakes}

@@

>>>>

\documentclass{article}
\usepackage{geometry}
%\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{standalone}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{siunitx}
\usetikzlibrary{patterns,snakes}

@@

\begin{table}[htbp]
\caption{Estimated Error Magnitudes for a \SI{100}{\milli\metre} field of view. Copied from MatchID.}
\label{tab:esterrmagn}
\begin{tabular}{@{}llr@{}} \toprule
2D Error	& Estimated Error (pixels)	& Notes \\ \midrule 
Contrast/Noise & 0.01 & Easiest to determine and minimize. \\
Interpolant Bias & 0.01 to 0.001 & Depends on noise and interpolant. \\
Lighting Variation & 0.005 & If using ZNNSD. \\
Subset size / Shape & linear fit to  &  Depends on underlying \\
 \hspace{.3cm} function & displacement field & displacement field.  \\
Optical distortions & 1+ & Depends on lens and distance moved.\\
 \hspace{.3cm} without corrections	&	& \\
Image Blur	& 0.001 & If blur is constant for all frames.\\
Turbulence/Shockwaves & $\sim$ 0.01 to 2+ & Depends on lightning and lab environment. \\
Out-of-Plane	& $\sim$ 0.5	& Depends on magnification and motion. \\
Lack of Perpendicularity	& $\sim$ 0.5	& Depends on tilt and motion. \\
System Resolution	& Small	& Increases subset size.\\
Aliasing	& $\sim$ 0.005	& Adds noise to the image.\\ \bottomrule
\end{tabular}
\end{table}
